simulate Hospitalizations

### 2023-01-26 5_roadmaps_future_projects/RSV_maternal_vac_eff/sim_H_Placebo.Rmd
add materials

**NOTE: time step here is in months--need to adjust seasonality accordingly**
```{r}
 start_time = 1 # start date (years)
 tmax = nrow((NL_B))
# end_time = 25 # end date (years)
my_times <- seq(start_time, tmax, by = 1) # gives a sequence from start to end
											 # in increments of 1
```

@@

###########################################
# 1/duration of maternal immunity (DAYS)
DurationMatVac= 60
DurationNaturalProtection= 30
###########################################

@@

PerCapitaBirthsMonth_total=rbind(do.call(rbind, replicate(6, PerCapitaBirthsMonth[7:18,], simplify=FALSE)),PerCapitaBirthsMonth[19:24,])
PerCapitaBirthsMonth_total=rbind(PerCapitaBirthsMonth_total,PerCapitaBirthsMonth)
PerCapitaBirthsMonth_total=rbind(PerCapitaBirthsMonth_total,PerCapitaBirthsMonth[327:328,])
#############################################

@@

#Save parameters in a list
```{r saveparms}
parms<-list(PerCapitaBirthsYear=PerCapitaBirthsMonth_total*12,
            DurationMatVac=DurationMatVac,
            WidthAgeClassMonth=WidthAgeClassMonth,
            um=um,
            b1=b1,
            phi=phi,
            rho1=rho1,
            rho2=rho2,
            dur.days1=dur.days1,
            dur.days2=dur.days2,
            dur.days3=dur.days3,
            yinit.matrix=yinit.matrix,
            baseline.txn.rate = baseline.txn.rate,
            q=q,
            c=c2,
            sigma1=sigma1,
            sigma2=sigma2,
            sigma3=sigma3,
            time.step='month',
            DurationNaturalProtection=DurationNaturalProtection
            )
```

@@

# number of hospitalizations depends on the season of observation 
# (birth to 90 days)
Hosp_vac_90 <- Hosp_90(t=101,H1)
# number of hospitalizations depends on the season of observation 
# (birth to 180 days)
#Hosp_vac_180 <- Hosp_180(t=90,H1)

# Vaccine efficacy 1-Hosp_mat_vac/Hosp_no_vac
1-Hosp_vac_90/Hosp_novac_90
```

>>>>

@@

###########################################
# 1/duration of maternal immunity (DAYS)
DurationMatVac= 0
DurationNaturalProtection= 30
###########################################

@@

PerCapitaBirthsMonth_total=rbind(do.call(rbind, replicate(6, PerCapitaBirthsMonth[7:18,], simplify=FALSE)),PerCapitaBirthsMonth[19:24,])
PerCapitaBirthsMonth_total=rbind(PerCapitaBirthsMonth_total,PerCapitaBirthsMonth)
PerCapitaBirthsMonth_total=rbind(PerCapitaBirthsMonth_total,PerCapitaBirthsMonth[327:328,])

PerCapitaBirthsYear_total=PerCapitaBirthsMonth_total*12
#############################################

@@

**NOTE: time step here is in weeks--need to adjust seasonality accordingly**
```{r}
 start_time = 1 # start date (years)
 tmax = nrow((NL_B))
# end_time = 25 # end date (years)
my_times <- seq(start_time, tmax, by = 1) # gives a sequence from start to end
											 # in increments of 1
```

#Save parameters in a list
```{r saveparms}
parms<-list(PerCapitaBirthsYear=PerCapitaBirthsYear_total,
            DurationMatVac=DurationMatVac,
            WidthAgeClassMonth=WidthAgeClassMonth,
            um=um,
            b1=b1,
            phi=phi,
            rho1=rho1,
            rho2=rho2,
            dur.days1=dur.days1,
            dur.days2=dur.days2,
            dur.days3=dur.days3,
            yinit.matrix=yinit.matrix,
            baseline.txn.rate = baseline.txn.rate,
            q=q,
            c=c2,
            sigma1=sigma1,
            sigma2=sigma2,
            sigma3=sigma3,
            time.step='month',
            DurationNaturalProtection=DurationNaturalProtection
            )
```

@@

# number of hospitalizations depends on the season of observation 
# (birth to 90 days)
Hosp_novac_90 <- Hosp_90(t=100,H1)
# number of hospitalizations depends on the season of observation 
# (birth to 180 days)
#Hosp_novac_180 <- Hosp_180(t=90,H1)

# Vaccine efficacy 1-Hosp_mat_vac/Hosp_no_vac
```
